Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2020-08-12 write-up/fda-recurrent.tex
about to edit missing data a bit shorter

The bootstrap followed by multiple imputation procedure has been studied extensively by~\cite{Bartlett2020} and is robust to uncongeniality.  The main disadvantage of this approach is its considerable computational intensity.  Recall likelihood calculations were computationally prohibitive by themselves, so combining with bootstrap and MI would further increase this large-scale computation.  The random subsampling framework thus simplifies handling of missing data via connections to function-on-scalar multiple imputation by~\cite{Petrovich2018} as well as to bootstrap to handle uncongeniality by~\cite{Bartlett2020}.

@@

In this section, we extend our model to the case of multilevel models with  functional regressors. Multilevel models are critical in mobile health where we expect high degree of individual variation.  In this case, we suppose that there is individual variation $b_i \sim N(0, \sigma_{b}^2)$ such that the multilevel extension of our model~\eqref{eq:hazard} is given by
\begin{equation}
\label{eq:multilevel}
h_i \left( t \given  H_{i,t}^{NX} ; \theta, b_i \right) \approx
\exp \left( Z_{t}^\top \gamma + g_t \left( H_{i,t}^{N} \right)^{\prime} \alpha
  + \left[ M_{i,t}^\top + C_{i,t}^\top J_{\hat \psi, \phi}\right] (\beta + b_i) \right)
= \exp \left( W_{i,t}^\top \theta  + Z_{i,t}^\top b_i \right),
\end{equation}
where $Z_Pi,t$

Ignoring the computational time of bootstrap sampling, the computational time of $200$ boostraps and $2$ imputations per boostrap leads to $35$ hours compared to $7$ hours.  Again, this highlights the substantial benefits of

@@

\section{Penalized logistic mixed-effects model}

>>>>

The bootstrap followed by multiple imputation procedure has been studied extensively by~\cite{Bartlett2020} and is robust to uncongeniality.  The main disadvantage of this approach is its considerable computational intensity.  Recall likelihood calculations were computationally prohibitive by themselves, so combining with bootstrap and MI would further increase this large-scale computation.  The random subsampling framework thus simplifies handling of missing data via connections to function-on-scalar multiple imputation by~\cite{Petrovich2018} as well as to bootstrap to handle uncongeniality by~\cite{Bartlett2020}. Ignoring the computational time of bootstrap sampling, the computational time for the first choise in the simulation study with $B=200$ bootstraps and $M=2$ imputations per bootstrap leads to $35$ hours for a sampling rate of $0.5$ compared to $7$ hours for a sampling rate of $4$.  This is simply to highlight the substantial benefits of the subsampling framework.

@@

In this section, we extend our model to the case of multilevel models with  functional regressors. Multilevel models are critical in mobile health where we expect high degree of individual variation.  In this case, we suppose that there is individual variation $b_i \sim N(0, \sigma_{b}^2)$ such that the multilevel extension of our model~\eqref{eq:hazard} is given by
\begin{equation}
\label{eq:multilevel}
h_i \left( t \given  H_{i,t}^{NX} ; \theta, b_i \right) \approx
\exp \left( Z_{t}^\top \gamma + g_t \left( H_{i,t}^{N} \right)^{\prime} \alpha
  + \left[ M_{i,t}^\top + C_{i,t}^\top J_{\hat \psi, \phi}\right] (\beta + b_i) \right)
= \exp \left( W_{i,t}^\top \theta  + Z_{i,t}^\top b_i \right),
\end{equation}
where $Z_{i,t} = M_{i,t} + C_{i,t} J_{\hat \psi, \phi}$. Lemma~\ref{lemma:logistic} implies that the random subsampling framework applied to equation~\eqref{eq:multilevel} leads to a penalized logistic mixed-effects model.  As far as the authors are aware, the combination of mixed-effects and $L_2$-penalization on a subset of parameters has not been addressed in existing packages.  To address this, we derive a penalized adaptive Gaussian quadarture (PADQ) for estimation.  For conciseness, this derivation is presented in Appendix~\ref{app:penlogit}.

@@

\section{Penalized logistic mixed-effects model}
\label{app:penlogit}
